Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-04-07 paper.tex
Craig doesn't like fairlys

This paper describes the scheduling problem. We present a constraint programming solution and
document how this model was constructed incrementally. We believe this illustrates how adaptable
constraint programming is, i.e.\ given a fairly robust model this can be incrementally developed to
address all of the required criteria. Our schedules are then constructed in a sequence of stages,
not dissimilar to the hybrid and decomposition based approaches in \cite{lombardi2012}. Some ISAF
published schedules are presented along with some of our own, some of these being new.  These
schedules are essentially blank forms, made available to event organisers, which can be filled in
with names of actual competitors, i.e.\ these schedules are reusable.

>>>>

This paper describes the scheduling problem. We present a constraint programming solution and
document how this model was constructed incrementally. We believe this illustrates how adaptable
constraint programming is, i.e.\ given a robust model this can be incrementally developed to
address all of the required criteria. Our schedules are then constructed in a sequence of stages,
not dissimilar to the hybrid and decomposition based approaches in \cite{lombardi2012}. Some ISAF
published schedules are presented along with some of our own, some of these being new.  These
schedules are essentially blank forms, made available to event organisers, which can be filled in
with names of actual competitors, i.e.\ these schedules are reusable.
